#Reproducible Research: Peer Assessment 1

by Vasilis Daroglou  
github repo with RMarkdown source code:  
https://github.com/VDaroglou/RepData_PeerAssessment1  
  
  
## Loading and preprocessing the data
1.  Set working direcory to the local repo directory.
2.  The data is read as a data variable type data frame.  
3.  **steps** column is converted to numeric type.(missing values are coded as NA)  
4.  **date** column is converted to Date type.  
5.  **interval** column is converted to numeric type.  
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv",
                     header=TRUE,
                     na.strings="NA",
                     colClasses=c("numeric", "Date", "numeric"))
```
Now, we can proceed with the data pre-examination of its str.
```{r}
str(activity)
```
   
## What is mean total number of steps taken per day?
For this part of the assignment, we can ignore the missing values in the 
data set.

We initiate with a pre-calculation of steps aggregation by day:
```{r}
steps_taken_per_day <- aggregate(steps ~ date, activity, sum)
colnames(steps_taken_per_day) <- c("date", "steps")
```
  
The following histogram displays the total number of steps taken per day, 
ignoring missing values.
```{r}
hist(steps_taken_per_day$steps,
     breaks = 20,
     col = "blue",
     main = "Histogram of Total Number of Steps Taken per Day",
     xlab = "Number of Steps per Day",
     ylab = "Number of times")
```
  
Finally,we calculate and report the mean and median of the total number of steps
taken per day:  
```{r mean_median}
mean_steps = mean(steps_taken_per_day$steps, na.rm=TRUE)
median_steps = median(steps_taken_per_day$steps, na.rm=TRUE)
```

The mean is **`r format(mean_steps)`** and 
the median is **`r format(median_steps)`**.
  
## What is the average daily activity pattern?
First, we calculate the aggregation of steps by intervals of 5-minutes 
and give names for columns of the result of this aggregation.
```{r}
steps_per_interval <- aggregate(steps ~ interval, activity, mean)
colnames(steps_per_interval) <- c("interval", "steps")

```
  
Then, we present below a plot with the time series of the average number
of steps taken (averaged across all days) versus the 5-minute intervals:
```{r}
plot(steps_per_interval, type = "l", 
     col = "dark blue",
     main = "Average Daily Activity Pattern",
     xlab = "Interval",
     ylab = "Number of steps")
```
  
Then, we calculate the 5-minute interval with the maximum number of steps,
on average across all the days in the dataset:
```{r}
steps_per_interval$interval[which.max(steps_per_interval$steps)]
```
This means that **08:35** is the 5-minute interval with the **maximum number of steps**,
on average across all the days.
  
## Imputing missing values
First calculate and report the total number of missing values in the dataset
(i.e. the total number of rows with NAs)
```{r na_count}
na_count = sum(is.na(activity))
na_count
```
So there are **`r format(na_count)`** of missing values in our dataset.
  
## Are there differences in activity patterns between weekdays and weekends?
  