#Reproducible Research: Peer Assessment 1

by Vasilis Daroglou  
github repo with RMarkdown source code:  
https://github.com/VDaroglou/RepData_PeerAssessment1  
  
  
## Loading and preprocessing the data
1.  The data is read as a data variable type data frame.  
2.  **steps** column is converted to Numeric type.(missing values are coded as NA)  
3.  **date** column is converted to Date type.  
4.  **interval** column is converted to factor type.  
```{r}
unzip("activity.zip")
activity <- read.csv("activity.csv",
                     header=TRUE,
                     na.strings="NA",
                     colClasses=c("numeric", "Date", "factor"))
```
Now, we can proceed with the data pre-examination of its str.
```{r}
str(activity)
```
  
## What is mean total number of steps taken per day?
For this part of the assignment, we can ignore the missing values in the data set.

We initiate with a pre-calculation of steps aggregation by day:
```{r}
steps_taken_per_day <- aggregate(steps ~ date, activity, sum)
colnames(steps_taken_per_day) <- c("date", "steps")
```
  
## What is the average daily activity pattern?


  
## Imputing missing values


  
## Are there differences in activity patterns between weekdays and weekends?
  